%%
%% In this note, we explain how to generate the low data in our paper
%% ``Holonomic gradient method for distribution function of 
%%   a weighted sum of noncentral chi-square random variables''
%%
%% To compile this TeX file, simply type the following command:
%%     latex note-en.tex && latex note-en.tex
%%

\iffalse
%\iftrue

\documentclass{article}

\else 

\documentclass[12pt]{article}

\textwidth 155 true mm
\textheight 247 truemm
\topmargin -0.4 true mm
\headheight 0 true mm
\headsep 0 true mm
\oddsidemargin 2.1 true mm
\evensidemargin 2.1 true mm
\footskip 5 true mm
%\titlesep 12pt

\fi

%\pagestyle{empty}

\usepackage{color}
%\usepackage{refcheck}
\usepackage{url}
%\usepackage{amssymb}
%\usepackage{amsmath}
%\usepackage{graphicx}
\usepackage{listings}

%\usepackage{amsthm}
%\newtheorem{theorem}{Theorem}
%\newtheorem{proposition}{Proposition}
%\newtheorem{lemma}{Lemma}
%\newtheorem{corollary}{Corollary}
%\newtheorem{conjecture}{Conjecture}
%\newtheorem{algorithm}{Algorithm}
%\theoremstyle{definition}
%\newtheorem{definition}{Definition}
%\newtheorem{example}{Example}

%% for shell script
\lstdefinestyle{BashInputStyle}{
  language=bash,
  firstline=2,% Supress the first line that begins with `%`
  basicstyle=\small\sffamily,
  numbers=left,
  numberstyle=\tiny,
  numbersep=3pt,
  frame=tb,
  columns=fullflexible,
  backgroundcolor=\color{white},
  linewidth=0.9\linewidth,
  xleftmargin=0.1\linewidth
}

\def\pd#1{\partial_{#1}}

\title{A Note for Numerical Experiments}
\author{Tamio Koyama}
\date{August, 2015}

\begin{document}
\maketitle
%\thispagestyle{empty}

\begin{abstract}
In this note, we explain how to generate the low data in our paper
\cite{koyama-takemura2}.
%,T.~Koyama, A.~Takemura, 
%``Holonomic gradient method for distribution function of 
%a weighted sum of noncentral chi-square random variables'',
%\url{http://arxiv.org/abs/1503.00378}.
\end{abstract}

\section{Preparation}
For our numerical experiments, we prepared C program {\tt program.c}, 
shell scripts 
{\tt tab1and2.sh}, {\tt tab3.sh}, {\tt tab4.sh}, {\tt tab5.sh},
and {\tt R} scripts 
{\tt fig1.R}, {\tt fig2.R}, {\tt tab1and2.R}, {\tt tab3.R}.
Our computer system is linux(debian), and we utilized GNU scientific library
BLAS, and {\tt R}.
The source file {\tt program.c} can be compiled by the following command:
\begin{lstlisting}[style=BashInputStyle]

gcc program.c -lm -lgsl -lblas -O0 -Wall 
\end{lstlisting}

 
In our numerical experiments, we generated the following files:
{\tt fig1.txt}, {\tt fig1.eps},
{\tt fig2.txt}, {\tt fig2-1.eps}, {\tt fig2-2.eps},
{\tt tab1and2.txt}, {\tt tab1and2.tex},
{\tt tab3.txt}, {\tt tab3.tex}, {\tt tab3.eps},
{\tt tab4.tex}, {\tt tab5.tex}.

\section{Synopsis}
\begin{verbatim}
./a.out S d r [s_1 s_2 ... m_1 m_2 ..]
\end{verbatim}
Our program mainly computes 
the ball probability
$$
\int_{x_1^2+\cdots x_d^2\leq r^2} \frac{1}{(2\pi)^{d/2}|\Sigma|}
\exp\left(-\frac{1}{2}(\mathbf x-\mu^\top\Sigma^{-1}(\mathbf x-\mu)\right)
d\mathbf x
$$
and the Fisher--Bingham integral
$$
\int_{\mathbf x\in S^{d-1}} \frac{1}{(2\pi)^{d/2}|\Sigma|}
\exp\left(-\frac{1}{2}(\mathbf x-\mu^\top\Sigma^{-1}(\mathbf x-\mu)\right)
|d\mathbf x|
$$
where $\Sigma=\mathrm{diag}(\sigma_1^2,\dots,\sigma_d^2)$,
$\mu=(\mu_1,\dots,\mu_d)^\top$ and 
$|d\mathbf x|$ is the volume element of $S^{d-1}(r)$.
\begin{itemize}
\item \verb+S+\/: Switch the behavior of the program. Behaviors are
  \begin{itemize}
    \item \verb+S=1+\ : %%    ball_prob();
    Compute the ball probability by HGM.
    \item \verb+S=2+\ : %%    ball_prob_graph();
    Compute the ball probability by HGM and output data for drawing graphs.
    \item \verb+S=3+\ : %%    fisher_bingham();
    Compute the Fisher--Bingham integral and it's differental by HGM.
    \item \verb+S=4+\ : %%    fisher_bingham_graph();
    Compute the Fisher--Bingham integral and it's differental by HGM
    and output data for drawing graphs.
    \item \verb+S=5+\ : %%    hirotsu_1_1();
    Generate data for Table 1 ($\Sigma^{(1)},\,\mu=0$).
    \item \verb+S=6+\ : %%    hirotsu_1_2();
    Generate data for Table 1 ($\Sigma^{(1)},\,\mu\neq 0$).
    \item \verb+S=7+\ : %%    hirotsu_2_1();
    Generate data for Table 1 ($\Sigma^{(2)},\,\mu=0$).
    \item \verb+S=8+\ : %%    hirotsu_2_2();
    Generate data for Table 1 ($\Sigma^{(2)},\,\mu\neq 0$).
    \item \verb+S=9+\ : %%    anderson_darling();
    Generate data for Table 2.
    \item \verb+S=10+\ : %%    comparison();
    Generate data for Table 3.
    \item \verb+S=11+\ : %%    feller();
    Generate data for Table 4.
  \end{itemize}
\item \verb+d+\/: Dimension.
\item \verb+r+\/: Radiaus of the ball or sphere.
\item \verb+s_1,...+\/: Parameters $\sigma_i$.
\item \verb+m_1,...+\/: Parameters $\mu_i$.
\end{itemize}


\section{How to Generate Low Data}
%In this section, we explain how to generate Figure 1 in \cite{koyama-takemura2}.
\noindent{\bf Figure 1}\/.
The following command generates the low data {\tt fig1.txt}
and eps file {\tt fig1.eps} for figure 1:
\begin{lstlisting}[style=BashInputStyle]

./a.out 2 3 20.0 3.0 2.0 1.0 1.0 0.5 0.25 > fig1.txt && R -f fig1.R
\end{lstlisting}

\medskip\noindent{\bf Figure 2}\/.
The following command generates the low data {\tt fig2.txt}
and eps files {\tt fig2-1.eps} and {\tt fig2-2.eps} for figure 2:
\begin{lstlisting}[style=BashInputStyle]

./a.out 4 3 20.0 3.0 2.0 1.0 1.0 0.5 0.25 > fig2.txt && R -f fig2.R
\end{lstlisting}

\medskip\noindent{\bf Table 1}\/.
Run the shell script {\tt tab1and2.sh}, then the low data {\tt tab1and2.txt} and 
the \TeX file {\tt tab1and2.tex} will be generated.

\medskip\noindent{\bf Table 2 and its figure}\/.
Run the shell script {\tt tab3.sh}, then the low data {\tt tab3.txt}, 
the TeX source {\tt tab3.tex}, and the eps file {\tt tab3.eps} will be generated.

\medskip\noindent{\bf Table 3}\/.
Run the shell script {\tt tab4.sh}, then the TeX source {\tt tab3.tex} will be
generated.

\medskip\noindent{\bf Table 4}\/.
Run the shell script {\tt tab5.sh}, then the TeX source {\tt tab5.tex} will be
generated.

%\iffalse
\iftrue

\begin{thebibliography}{1}

\bibitem{koyama-takemura2}
T.~Koyama and A.~Takemura.
\newblock Holonomic gradient method for distribution function of a weighted sum
  of noncentral chi-square random variables.
\newblock \url{http://arxiv.org/abs/1503.00378}, 2015.

\end{thebibliography}

\else

\bibliographystyle{plain}
\bibliography{reference}

\fi

%\appendix
\end{document}
